How did the introduction of Stemmed Points affect Mobility and Site Occupation during the Late Pleistocene in Korea?

### 2020-12-17 analysis/paper/paper.Rmd

```{r climate-model, fig.cap="Mean Annual Temperature (MAT) of the Korean Paleolithic assemblages mentioned in this research. A: Site locations on the map and MAT. B: MAT distributions for each site during the period they were occupied. C: MAT from 50ka to 10ka. The grey lines indicate the MAT for each site and the black line is the mean temperature of all sites. The light grey area in the middle of the plot indicates the duration of MIS 2, separating MIS 3 and 1, and dark grey area represents the duration of LGM. D: The relationship between MAT and site elevation. The blue line is a linear regression on elevation and MAT with the grey area showing the 95% confidence interval.t.", cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/007-climate-model-plots.R"))}
quietly(source(here::here("analysis/paper/007-climate-model-plots.R")))
knitr::include_graphics(here::here("analysis/figures/007-climate-model-sites-panel-plot.png"))
```

>>>>

```{r climate-model, fig.cap="Mean Annual Temperature (MAT) of the Korean Paleolithic assemblages mentioned in this research. A: Site locations on the map and MAT. B: MAT distributions for each site during the period they were occupied. C: MAT from 50ka to 10ka. The grey lines indicate the MAT for each site and the black line is the mean temperature of all sites. The light grey area in the middle of the plot indicates the duration of MIS 2, separating MIS 3 and 1, and dark grey area represents the duration of LGM. D: The relationship between MAT and site elevation. The blue line is a linear regression on elevation and MAT with the grey area showing the 95% confidence interval.", cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/007-climate-model-plots.R"))}
quietly(source(here::here("analysis/paper/007-climate-model-plots.R")))
knitr::include_graphics(here::here("analysis/figures/007-climate-model-sites-panel-plot.png"))
```
